A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-04-22 paper.tex
Added explanation of the example

>>>>

First, we introduce a running example to assist the explanation. We consider a
simple arbiter system in which the environment requests for either 1 or 0
resources, and the controller may grant access to two resources. The controller
must ensure that the number of unhandled requests is not $\geq 2$.
Figure~\ref{fig:example} shows the variables (\ref{fig:examplevars}) and the
formulas for computing next-state variables (\ref{fig:exampletrans}) for this
example.

\begin{figure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \begin{tabular}{l | l | l}
            \textbf{Controllable} & \textbf{Uncontrollable} & \textbf{State} \\
            \hline
            \texttt{request = \{0, 1\}} & \texttt{grant0 = \{0, 1\}} & \texttt{resource0 = \{0, 1\}} \\
            & \texttt{grant1 = \{0, 1\}} & \texttt{resource1 = \{0, 1\}} \\
            & & \texttt{nrequests = \{0, 1, 2, 3\}} \\
        \end{tabular}
        \caption{Variables}
        \label{fig:examplevars}
    \end{subfigure}

    \begin{subfigure}[t]{\textwidth}
        \begin {align*}
            \texttt{resource0'} & \texttt{ = grant0;} \\
            \texttt{resource1'} & \texttt{ = grant1;} \\
            \texttt{nrequests'} & \texttt{ = (nrequests + request >= resource0 + resource1)} \\ 
                                & \texttt{ ? (nrequests + request - resource0 - resource1) : 0;}
        \end{align*}
        \caption{Transition Relation}
        \label{fig:exampletrans}
    \end{subfigure}
    \caption{Example}
    \label{fig:example}
\end{figure}
